---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Seokhoon Shin"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = Date, y = Cases_Asian, color = Cases_Asian) ) + geom_point() 
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_race |> 
  filter(state == "MA") |> 
  ggplot(aes(x = Total_count, y = Asian_count, color = Asian_count)) + geom_line()
```

1. Write code for a plot and describe what you observe?
ggplot(covid_data_orig, aes(x = Date, y = Cases_Asian, color = Cases_Asian) ) + geom_point()
Based on the code and the graph shown above, it appears that as time passes, the total number of Covid-19 cases among the Asian population is increasing. The plot should express an upward trend of Covid-19. 

2. Are there any conclusions you can draw?
It seems like the total number of Covid-19 cases are increasing every month. Which expresses an upward trend of Covid-19. 

3. What were you not able to do due to not having the R knowledge?
I was not able to create a detailed graph which includes more than 3 different categories. 

4. What other data would be useful to better understand this data?
Age Data :  Age distribution of Covid-19 cases would be useful to provide more detailed trends to the viewers. 
Environmental Data :  Environmental aspects would be useful to the viewers with deeper insights.  



